\newpage
\section{Intro to self and the workplace}

\subsection{Description}
Tell the reader about you and your work. Include relevant features of yourself, including your learning objectives for this internship, if your background and prior experience had an impact, etc, and include relevant features of your work (role title \& supervisor title, how your unit fits within the organization, location of the internship (e.g. local or international), describe your role and key activities as if to someone unfamiliar with this field, etc).

\subsection{Content}

\subsubsection{About me}
I am currently a third year Computer Science student at Concordia. 
My focus area in the field is Software Systems. 
With the nature of my study, I am eager to learn about Software Development process in depth, from starting point to shipping final product.
Before the internship, mostly I was doing personal projects on my own and sometimes in team.
I also enjoy participating in Hackathons just because it is fun and I have a chance to meet like-minded people.

\subsubsection{About Theia team at Ericsson}
Ericsson is a multinational networking company and is also a major leader in the domain of telecommunications technology, headquarterd in Stockholm.
Theia team fits in the organization as a software team mainly responsible for maintaining and developing project Eclipse Theia (https://theia-ide.org)
which is a framework to develop Cloud and Desktop IDE (Integrated Development Environment).
Along with the main repository (code base), the team also works on a variety of support tools.

\begin{itemize}
    \item Main repository: https://github.com/eclipse-theia/theia
    \item https://github.com/theia-ide 
    \item https://github.com/eclipse-theia
\end{itemize}


The project is open-source, hence the code base is public and available on GitHub.
With the nature of open-source project, contribution comes from anywhere and anyone.
Theia team at Ericsson is only one of the teams contributing to the project, along side with many other companies such as Typefox, SAP, RedHat, Huawei, etc.
\\
\\
With the current COVID-19 pandemic and Canada regulations, all the activities in the internship is done \textbf{remotely (work from home) }

\subsubsection{About my role in Theia team}
My role as a Coop Software Developer is to develop, enhance features in the framework, and participating in code review for both team's members and community contributors.
The team is very flexible on the tasks I can work with. I am allowed to work on issues that I find interesting.



