\newpage
\section{Application from classroom to workplace}

\subsection{Description}

\begin{itemize}
    \item How does this internship experience fit (or not) with your program of study? How did it align with your expectations? Provide concrete examples.
    \item How did you apply knowledge, concepts or skillsets learned from your coursework, labs or projects during your internship? Which course(s) helped you?
    \item What challenges did you experience in applying the theories and concepts you learned in class in the workplace? What differences or similarities did you notice? Why do you think this was the case?
\end{itemize}

\subsection{Content}

\subsubsection{How this internship fits with the program of study}
My program of study is Computer Science (Software Systems option). The internship fits with my study and my passion for software.
I'm also a fan of open-source culture so working in an open-source project has always been one of my goals.

\subsubsection{Knowledge applied to workplace}
Before the internship, I've done several web development projects, that helped me on understanding and getting familiar with the job at first. Also, I've had some experience with Docker containerizing before, so I was confident working with the Docker images of theia-apps.
\\
My personal projects and Hackathon experience were the foundation for me to start working with the team.
The courses I took so far at Concordia were mostly theoretical.
They helped students to understand the basics of computer science, but are not very useful when working in a workplace environment.
