\newpage
\section{Moving forward}

\subsection{Description}

\begin{itemize}
    \item How did this internship help you gain more clarity about your academic and career path? What is your biggest takeaway from this internship experience? What is important to you in a professional work environment?
    \item Share something you accomplished or are proud of. Why is this important to you? What about this task/project/ experience do you want to repeat after this internship? If you were coaching another student to be successful in this organization/position, what advice would you give them?
    \item What actions will you take as you plan and prepare for your next internship, study term or career move? 
\end{itemize}


\subsection{Content}

\subsubsection{Career path}
I appreciate the opportunity that brought me to Ericsson. 
It's my first internship in the software field and I've learned so much from working here in the past few months.
One of the key takeaways from this experience for me would be little details matter.
I've practiced to be a more considerate developer, carefully choosing between the possible options when encountering a problem to ensure the most efficient outcome.

\subsubsection{After the internship}
Working in Theia is the first time I contribute to a big open-source project.
It's something I have always wanted to do before. 
Furthermore, working in the project, I had the chance to observe and work on every aspect of software development.
I have been implementing features in both front-end and back-end.
I also learned to write unit tests for the test suite of the project.
Along with that, I learned and applied knowledge of CI-CD into a real-world application.
That's something I value and wish I have the chance to do more in the future, after this internship. 
\\
A piece of advice I would give other students for the same role is to ask questions and don't be hesitant to do so.
That's the only way interns can get familiar with the team and understand the project better.
\\





